Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-05-18 revisionMemo/rev1.tex
cleanup

		\item \textcolor{blue}{ \emph{ MG/CD: We think the reviewer makes a good suggestion here to clarify, mathematically or in some other illustrative way, exactly how we think that dependencies bias the estimator. For example we can say that our target of inference is the estimation of beta (with some variance). If a coefficient is correlated with a dependency, then we could obtain an estimate for beta that is artificially high (and the same is true for the reverse).}}
	\item  \textcolor{blue}{ \emph{ What we think: True DGP: $Y = B0 + XB1 + a + b +$ 3rd order stuff + e
	\item What most do: $Y = \hat{B0} + X\hat{B1} + e$
	\item Something like if we have dependencies then $E(\hat{B1}) = E(B1) + cov(B1,$ other stuff)
	\item SM: needs to add more here to indicate how the existing simulation section is meant to deal with this issue ... onus is on SM to bring in the problems that we highlight in the simulation section to section 2, so readers are clearer on the problem that we are trying to address

@@

		\item It is useful to think of the infeasible estimator and the implications for interpreting the LFM component.  The infeasible estimator takes the transformation f(.), fixed effects parameters, and SRRM random effects as know, in which case the LFM amounts to predictions from a factor model fit to the adjacency matrix of residuals on the scale of the latent outcome.  Would this be a reasonable interpretation? If so it would be useful to draw the connection to factor models commonly in use these days (such as the interactive fixed effects model of Bai, which is the basis of, e.g., generalized synthetic control methods).

@@

		\item \emph{\textcolor{blue}{As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions? We address this in the section concerning the simulation and Aronow's approach. \textbf{SM we need to add more here}}} 

>>>>

		\item \textcolor{blue}{ \emph{ We think the reviewer makes a good suggestion here to clarify, mathematically or in some other illustrative way, exactly how we think that dependencies bias the estimator. For example we can say that our target of inference is the estimation of beta (with some variance). If a coefficient is correlated with a dependency, then we could obtain an estimate for beta that is artificially high (and the same is true for the reverse).
	\item \textcolor{blue}{ \emph{ Additionally, we have SM: needs to add more here to indicate how the existing simulation section is meant to deal with this issue ... onus is on SM to bring in the problems that we highlight in the simulation section to section 2, so readers are clearer on the problem that we are trying to address

@@

		\item It is useful to think of the infeasible estimator and the implications for interpreting the LFM component.  The infeasible estimator takes the transformation f(.), fixed effects parameters, and SRRM random effects as known, in which case the LFM amounts to predictions from a factor model fit to the adjacency matrix of residuals on the scale of the latent outcome.  Would this be a reasonable interpretation? If so it would be useful to draw the connection to factor models commonly in use these days (such as the interactive fixed effects model of Bai, which is the basis of, e.g., generalized synthetic control methods).

@@

			As for (b), the reviewer raises an important point. How well does AME work out when the DGP does not abide by parametric assumptions? We address this in the section concerning the simulation and Aronow's approach. }}
